Proposed Solution

### 2016-11-14 Ennan-Proposal/intro.tex

Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
Tools which detect misconfigurations at compile time often require the user to explicitly define constraints, a time consuming and error prone task.
We propose a framework to statically verify configuration files based on automatically generated constraints that define a correct file.
The core idea is to analyze many examples of configuration files from widely available datasets and derive a language model (a set of constraints) that can be used to verify new configuration files.

>>>>

\section*{\app: Automated Verification of Configuration Files}
\paragraph{Overview:} 
Configuration errors (also known as misconfigurations) have become one of the major causes of system failures, resulting in security vulnerabilities, application outages, and incorrect program executions. 
Configuration errors were reported to be the largest fraction of failures in storage systems in a 2014 industry survey. 
Although many techniques have been proposed for configuration error detection, these approaches mainly can only be applied after an error has occurred.
Tools which detect misconfigurations at compile time often require the user to explicitly define constraints, a time consuming and error prone task.
We propose a framework to statically verify configuration files based on automatically generated constraints that define a correct file.
The core idea is to analyze many examples of configuration files from widely available datasets and derive a language model (a set of constraints) that can be used to verify new configuration files.
